\chapter{Thoughts on further development}

\section{''Open file'' --dialog}

If no scripts are given as parameters when starting Moai Qt Host, the files could be inquired from the user via a dialog.
Providing this feature would require changes to the script-module. The actual dialog could be easily implemented with Qt.

\section{Mobile OS support}

Qt supports several mobile operating systems, like Symbian and MeeGo. 
Support for Android and iOS environments is being planned.
Thus, using Qt-libraries on these platforms to provide required functionality for Moai Qt Host should be possible.

The host-part of Moai Qt Host should be portable to mobile devices with relatively small changes. 
Larger problem is the Moai SDK itself, which must be compiled for target operating systems. 
Perhaps the easiest way to do this would be to compile the Moai SDK with Qt Creator (refer to section~\ref{qtproject}).

\section{Separating input handling from the window-module}

Mobile operating systems might require some changes to the way the input is currently handled.
Required changes could be done within the current window-module, but this might cause some unnecessary features to be included in desktop and mobile environments.

Another way would be to use different input modules for desktop and mobile environments.
This would require separating the input handling from the current window-module.
One way to implement this would be to create a transparent widget over the main window, and have that widget act as the input module.

\section{Sensor support for mobile systems}

If support for mobile operating systems is provided, it would also be preferable that all the related sensors (compass, location, etc.) are supported as well.
This would require changes to the window-module of Moai Qt Host, but the changes themselves should be quite simple.
Sensors supported by Moai SDK can be found by examining the AKU-interface.

\section{Dynamic script reloading}

GLUT-host gives user the ability to reload .lua-files when they are modified during runtime.
This is a very useful feature when using the host when developing your game.

Ideally this same functionality would be implemented to Moai Qt Host by using Qt. This would keep the implementation same for all platforms. 
The script-module needs to be modified, but there should be no need to touch the other modules. 
If a timer is required, we can just make a new one inside the script-module, instead of using the one in window-module.
Enabling script reloading could be done the same way as it is done in GLUT-host, which is with an e-flag in parameters when starting the host.
