\chapter{Introduction}
\label{chap:quick}

\section{Purpose and coverage}

The purpose of this document is to serve as a maintenance guide for Moai Qt Host application.

The target audience of this document is anyone who is interested in developing, modifying or using Moai Qt Host.

\section{Product and environment}

The product Moai Qt Host is a host application for Moai SDK. 
The primary task of the application is to offer the OpenGL drawing surface and relay user input to the Moai engine. 
Game developers using Moai are the primary users of Moai Qt Host.

Moai Qt Host is designed for desktop environments including Windows, OS X and Linux. It is designed for development and release of games, essentially replacing the GLUT host by offering better performance.

\section{Definitions, terms and abbreviations}

The definitions, terms and abbreviations are listed in table ~\ref{deftable}. 

\begin{table}[h!]
\begin{center}
\caption{Terms and abbreviations}
\label{deftable}
	\begin{tabular}{|l|p{0.75\textwidth}|}
	\hline
	Term & Explanation \\ 
	\hline \hline
	AKU & Moai SDK API for host application. \\
	\hline
	Application & In this document application refers to Moai Qt Host application. \\
        \hline
	C++ & Programming language.\\
	\hline
	FMOD & Platform independent audio system.\\
	\hline
        GLUT host & An OpenGL demo Moai host that runs on Windows, OSX and Linux. It's not supposed to be used for development. \\
        \hline
	Host & In this document a host is an interface application between a device and the Moai game engine.\\
	\hline
	Lua & A scripting language\\
	\hline
	Moai / Moai SDK & 2D game development environment\\
	\hline
	OpenGL & Open Graphics Library is a platform independent graphics library. \\
	\hline
	Qt & Platform independent software anf graphical user interface development environment.\\
	\hline
	Terminal & Textual command interface.\\
	\hline
        UNTZ & Open source audio library.\\
	\hline
	\end{tabular}
\end{center}
\end{table}

\section{References}

\begin{enumerate}
\item\label{itm:qtlicense} Qt Licensing. [accessed on 15.10.2012]. Available at:
  \url{http://qt.digia.com/Product/Licensing/}
\item\label{itm:mpl} Mozilla Public License version 2.0. [accessed on 04.02.2013]. Available at:
  \url{http://www.mozilla.org/MPL/2.0/}
\end{enumerate}

\section {Document overview}

Chapter two contains application overview.

Chapter three contains information on application environment.

Chapter four contains information on maintenance staff and maintenance tools.

Chapter five contains an overview or the implementation of Moai Qt Host.

Chapter six contains information on files and components.

Chapter seven contains maintenance instructions.

Chapter eight contains infromation on reporting and documents.

Chapter nine contains information on known problems, curiosities and illogicalities.

Chapter ten contains abandoned alternative solutions.

Chapter ten contains thoughts on further development.
