\chapter{Application environment}
\label{chap:using}

\section{Hardware environment}

Any hardware capable of running supported operating systems is adequate to run Moai Qt Host. Currently Moai officially supports only OpenGL 2.0 so any OpenGL features that are on newer versions of OpenGL won't work. A keyboard and a pointer device such as a mouse are required.

\section{Software environment}

The application has tested versions for Windows 7, OS X Mountain Lion and Ubuntu Linux 12.04.

\subsection{Programming language}

The application is implemented with C++.

\subsection{Compiler}

The application was compiled with Qt Creator, so Qt MOC compiler was used. Furthermore following compilers were used on different platforms to compile Moai SDK: Microsodt Visual Studio 2010 compiler on Windows, GCC on Linux, GCC and Clang on OS X.

\subsection{Browsers}

The application requires no web browser.

\subsection{Database}

The application does not use a database.

\section{Network environment}

No network connectibility is required to run or install the application.

\section{Third-party software and components}

Third-party components are listed in table ~\ref{component_table}.

\begin{table}[h!]
\begin{center}
\caption{Third-party components}
\label{component_table}
	\begin{tabular}{|l|c|c|}
	\hline
	Component & Version\\ 
	\hline \hline

	Moai SDK & 1.3 (Build 160)\\
	\hline
	Qt Creator & 2.4.1\\
	\hline
	Qt libraries & 4.8.1\\
	\hline
	Qt SDK & 1.2.1\\
	\hline
	\end{tabular}
\end{center}
\end{table}
\section{Compatibility}

The application is compatible with above-mentioned operating systems and third-party components.
